---
title: "Homework 2: Outlier Detection Review"
author: "Chenthuran Abeyakaran"
date: "2/27/2020"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(OutlierDetection)
library(OutliersO3)
library(outliers)
```

# Read and Summarize Data
Apply the technique discussed above to the data set that you are using as part of the your problem. Please make sure to report the following:

a) summary of you data sets
Consider using summary function and use graphics to display your data
```{r}
full = read.csv("data/data.csv")
full
```

```{r}
data <- full[, c("acousticness", "danceability", "energy", "key", "instrumentalness", "mode", "liveness", "loudness", "speechiness", "tempo", "valence")]
data <- data[complete.cases(data), ]
data
```

```{r}
summary(data)
```

```{r}
boxplot(data$acousticness, ylab="Acousticness")
boxplot(data$danceability, ylab="Danceability")
boxplot(data$energy, ylab="Energy")
boxplot(data$instrumentalness, ylab="Instrumentalness")
boxplot(data$liveness, ylab="Liveness")
boxplot(data$loudness, ylab="Loudness")
boxplot(data$speechiness, ylab="Speechiness")
boxplot(data$tempo, ylab="Tempo")
boxplot(data$valence, ylab="Valence")

hist(data$key, xlab="Key (Numeric Mapping)")
hist(data$mode, xlab="Mode")
```

# Remove Outliers
b) Apply all the outlier detection methods described above to your data set as they fit

```{r}
density_out <- dens(data, k=0.001*nrow(data), cutoff=0.999)
density_out
```

```{r}
maha_out <- maha(data, cutoff = 0.9999995)
maha_out
```

c) Report outlier based on consensus rule based on all the techniques that applied to your data sets.

```{r}
outliers_ind <- Reduce(intersect, list(density_out$`Location of Outlier`, maha_out$`Location of Outlier`))

full[outliers_ind, c("name", "artists")]
```
```{r}
cleaned <- full[-c(20054, 24493, 36830, 38621, 40414, 56642, 56715, 60975, 73050, 74591, 75352, 78142, 91715, 92469, 92553, 93225, 108942, 124134, 124588, 141208, 141459, 142955, 152962, 154618, 154919, 156805, 164676, 169585, 169872, 169969, 170021), ]

cleaned
```
```{r}
write.csv(cleaned, "data/cleaned_songs.csv")
```











